---
title: "Coding Challenge 4"
author: "Doug Terza"
date: "2026-02-19"
output:
  html_document:
    theme: sandstone
    toc: true          
    toc_depth: 3       
    toc_float: true
    code_folding: hide
  md_document:
    variant: gfm
  word_document:
  pdf_document:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
library(ggplot2)
library(ggpubr)
```

# Question 1
## Explain the following

### a. YAML Headers
A YAML header providers the render markdown with a title, author, and date. It also provides selection of the type of 
output the render with be such as html, word, or pdf document. Global commands are also available such as hiding th R 
chunks when rendered.

### b. Literate programming
Literate programming is writing code in a way that alows for machine rendering to be read and understood by a
human. R markdown is an example of this.

# Question 2
## Take the code you wrote for coding challenge 3, question 5, and incorporate it into your R markdown file. 
### a. Check out the paper here 
[i.	Noel, Z.A., Roze, L.V., Breunig, M., Trail, F. 2022. Endophytic fungi as promising biocontrol agent to protect wheat from Fusarium graminearum head blight. Plant Disease.](https://doi.org/10.1094/PDIS-06-21-1253-RE)

### b. Reading in the data csv file with a relative path
```{r b}
knitr::opts_chunk$set(warning = FALSE)
data.toxin <- read.csv("MycotoxinData.csv", na.strings = "na")
data.toxin$Treatment <- factor(data.toxin$Treatment, levels = c("NTC", "Fg", "Fg + 37", "Fg + 40", "Fg + 70"))
str(data.toxin)
```

### c. Make a separate code chunk for the figures plotting the DON data, 15ADON, and Seedmass, and one for the three combined using ggarrange. 
```{r c}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

toxin.box4<- ggplot(data.toxin, aes(x = Treatment, y = DON, fill = Cultivar))+ 
  geom_boxplot(color= "#000000", position = position_dodge(width = 0.85))+ 
  scale_fill_manual(values = c("#56B4E9", "#009E73"))+ 
  geom_point(shape = 21, color = "#000000", alpha = 0.6, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.85))+ 
  ylab("DON (ppm)")+ 
  xlab("")+ 
  scale_color_manual(values = c(cbbPalette[[3]], cbbPalette[[4]]), name = "Cultivar", labels = c("Ambassador", "Wheaton"))+
  theme_classic()+ 
  facet_wrap(~Cultivar)
toxin.box4

toxin.box5<- ggplot(data.toxin, aes(x = Treatment, y = X15ADON, fill = Cultivar))+ 
  geom_boxplot(color= "#000000", position = position_dodge(width = 0.85))+
  scale_fill_manual(values = c("#56B4E9", "#009E73"))+
  geom_point(shape = 21, color = "#000000", alpha = 0.6, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.85))+
  ylab("DON (ppm)")+
  xlab("")+
  scale_color_manual(values = c(cbbPalette[[3]], cbbPalette[[4]]), name = "Cultivar", labels = c("Ambassador", "Wheaton"))+
  theme_classic()+
  facet_wrap(~Cultivar)
toxin.box5

toxin.box6<- ggplot(data.toxin, aes(x = Treatment, y = MassperSeed_mg, fill = Cultivar))+ 
  geom_boxplot(color= "#000000", position = position_dodge(width = 0.85))+
  scale_fill_manual(values = c("#56B4E9", "#009E73"))+
  geom_point(shape = 21, color = "#000000", alpha = 0.6, position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.85))+
  ylab("DON (ppm)")+
  xlab("")+
  scale_color_manual(values = c(cbbPalette[[3]], cbbPalette[[4]]), name = "Cultivar", labels = c("Ambassador", "Wheaton"))+
  theme_classic()+
  facet_wrap(~Cultivar)
toxin.box6

toxin.box7<- ggarrange(toxin.box4, toxin.box5, toxin.box6,
                       labels = "auto",
                       nrow = 1,
                       ncol= 3,
                       common.legend = TRUE)
toxin.box7

toxin.box8<-ggarrange((toxin.box4+
  geom_pwc(aes(group = Treatment), method = "t_test", label = "{p.adj.format}{p.adj.signif}")),
  toxin.box5+
  geom_pwc(aes(group = Treatment), method = "t_test", label = "{p.adj.format}{p.adj.signif}"),
  toxin.box6+
  geom_pwc(aes(group = Treatment), method = "t_test", label = "{p.adj.format}{p.adj.signif}"),
  labels = "auto",
  nrow = 1,
  ncol = 3,
  common.legend = TRUE)
toxin.box8
 
```

# Question 3
## Knit your document together in the following formats: 
### a. Format selection
Within the YAML header I chose an html format; 
 output: 
  html_document
### b. GitHub flavored markdown 
 md_document:
    variant: gfm

# Question 4
## Push the .docx or .pdf and .md files to GitHub inside a directory called Coding Challenge 4.
Created a new repository specifically for this assignment

# Question 5
## Now edit, commit, and push the README file for your repository and include the following elements.
### a. A clickable link in your README to your GitHub flavored .md file
### b. A file tree of your GitHub repository.

# Question 6
## Please turn in the file generated in question 3a to canvas with a clickable link to your GitHub repository within the document. 


